### 2009-04-02 talk/icooolps2009-dotnet/clibackend.tex
copy the introduction from the ecoop paper, and adapt it to this one. Add few XXXs

\section{The CLI backend for the Generated JIT}
\label{sec:clibackend}

@@

For a large part, implementing the CLI backend is easy and straightforward, as
there is a close corrispondence between most of the operations used by
frontend's flowgraphs and the CLI instructions.  Thus, we will not dig into
details for this part.

@@

When a new case is added to a flexswitch, the backend generates the new blocks
into a new single method.  The newly created method is pointed by a
delegate\footnote{\emph{Delegates} are the .NET equivalent of function
  pointers.} stored in the flexswitch, so that it can be invoked later when
needed.

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link of the block dynamically added in the right-hand side
picture of Figure~\ref{flexswitch-fig}. How it is possible to jump in 
the middle of a method?

>>>>

\section{The CLI JIT backend}
\label{sec:clibackend}

@@

For a large part, implementing the CLI backend is easy and straightforward, as
there is a close correspondence between most of the operations used by
frontend's flowgraphs and the CLI instructions.  Thus, we will not dig into
details for this part.

@@

When a new case is added to a flexswitch, the backend generates the new blocks
into a new single method.  The newly created method is pointed to by a
delegate\footnote{\emph{Delegates} are the .NET equivalent of function
  pointers.} stored in the flexswitch, so that it can be invoked later when
needed.

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link of the block dynamically added in the right-hand side
picture of Figure~\ref{flexswitch-fig}. How is it possible to jump into
the middle of a method?

### 2009-04-02 talk/icooolps2009-dotnet/intro.tex
copy the introduction from the ecoop paper, and adapt it to this one. Add few XXXs

PyPy's approach \cite{RiBo07_223} is to automatize the generation of JIT compilers in order
to minimize the effort required to get a fast implementation of a
dynamic language; automatic generation of JIT compilers is done with
the help of partial evaluation techniques and requires the user only
to provide an interpreter with some manual annotations which hint
the generator how interpretation and JIT compilation has to be interleaved.

@@

The contributions of this paper are twofold: (1) \emph{promotion} is a
generalization of polymorphic inline caches that make partial evaluation
practical for dynamic languages; (2) we demonstrated that the idea of
\emph{JIT layering} can give good results, as dynamic languages can be even
faster than their static counterparts.

\subsection{PyPy and RPython}

\commentout{
\begin{figure}[h]
\begin{center}
\includegraphics[width=.6\textwidth]{diagram0}
\caption{PyPy infrastracture for generating an interpreter of a
  language $L$ for several platforms}\label{pypy-fig}
\end{center}
\end{figure}
}

@@

One of the most important aspects that PyPy's translation toolchain can weave
in is the \emph{automatic generation of a JIT compiler}.  This section will
give a high-level overview of how the JIT-generation process works. More
details will be given in subsequent sections.

@@

It is important to distinguish between three distinct phases of execution:

@@

Note that in this schema translation-time happens only once, on the
developer's machine.  By contrast, compile-time and runtime happens every time
the user wants to run some program.

@@

Later, when the generated code is executed, the callback might be hit and the JIT
compiler is restarted again.  At this point, the JIT knows exactly the state
of the program and can exploit all this extra knowledge to generate highly
efficient code.  Finally, the old code is patched and linked to the newly
generated code, so that the next time the JIT compiler will not be invoked
again.  As a result, \textbf{runtime and compile-time are continuously
interleaved}. The primitive to do this sort of interleaving is called promotion,
it is described in Section \ref{sec:promotion}.

One of the most important optimizations that the generated JIT does is removing
unnecessary allocations. This is described in Section \ref{sec:virtuals}

@@

>>>>

PyPy's approach \cite{RiBo07_223} is to automatize the generation of 
specializing JIT compilers in order
to minimize the effort required to get a fast implementation of a
dynamic language; automatic generation of JIT compilers is done with
the help of partial evaluation techniques and requires the user only
to provide an interpreter with some manual annotations which hint
the generator how interpretation and JIT compilation has to be interleaved \cite{PyPyJIT09}.

@@

The main contribution of this paper is to demonstrate that the idea of
\emph{JIT layering} can give good results, as dynamic languages can be even
faster than their static counterparts.

\subsection{Overview of PyPy}

@@

One of the most important aspects that PyPy's translation toolchain can weave
in is the \emph{automatic generation of a JIT compiler}.  This section will
give a high-level overview of how the JIT-generation process works. More
details can be found in \cite{PyPyJIT} and \cite{PyPyJIT09}.

@@

\anto{maybe we can avoid to talk about hints?}

\commentout{
It is important to distinguish between three distinct phases of execution:

@@

Note that in this schema translation-time happens only once, on the
developer's machine.  By contrast, compile-time and runtime happens every time
the user wants to run some program.
}

@@

Later, when the generated code is executed, the callback might be hit and the JIT
compiler is restarted again.  At this point, the JIT knows exactly the state
of the program and can exploit all this extra knowledge to generate highly
efficient code.  Finally, the old code is patched and linked to the newly
generated code, so that the next time the JIT compiler will not be invoked
again.  As a result, \textbf{runtime and compile-time are continuously
interleaved}.

\commentout{
The primitive to do this sort of interleaving is called promotion,
it is described in Section \ref{sec:promotion}.

One of the most important optimizations that the generated JIT does is removing
unnecessary allocations. This is described in Section \ref{sec:virtuals}
}

@@

\anto{XXX: we need to explain what is a flexswitch!}

### 2009-04-02 talk/icooolps2009-dotnet/paper.tex
copy the introduction from the ecoop paper, and adapt it to this one. Add few XXXs

@@

\section{Introduction}
XXX
\cite{PyPyJIT09}

\section{PyPy and automatic JIT compiler generation}
XXX

\include{clibackend}
\input{benchmarks}
\input{conclusion}

>>>>

\lstset{language=Python,
        basicstyle=\scriptsize\ttfamily,
        keywordstyle=\color{blue}, % I couldn't find a way to make chars both bold and tt
        frame=none,
        stringstyle=\color{blue},
        fancyvrb=true,
        xleftmargin=20pt,xrightmargin=20pt,
        showstringspaces=false}

@@

\input{intro}
\input{clibackend}
\input{benchmarks}
\input{conclusion}
